Spin-orbit misalignment for the long period companion of KOI-368

### 2013-07-01 msV0.tex
add in new figures and references

\documentclass[apjl]{emulateapj}

\shorttitle{shorttitle}
\shortauthors{shortauthors}

%%% packages
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
%\usepackage{array}
\usepackage{lineno}

@@

@@

@@

\section{Discussion}
\label{sec:discussion}

>>>>

\documentclass[preprint]{emulateapj}
\input{newcommand_gen.tex}
\shorttitle{shorttitle}
\shortauthors{shortauthors}

%%% packages
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{subfigure}
%\usepackage{array}
\usepackage{lineno}

@@

%Kepler Obliquity measurement
\citet{Hirano:2012} 
using the rotation period from the lightcurve and 
then combined with the projected rotation period and stellar radius from 
high-res spectrospcopy, measured the obliquity of 15 KOI systems.

\citet{Barnes:2011} use the asymmetry in the Kepler transit lightcurve of KOI-13 
to measure the spin-obital alignment angle.

@@

{\bf KOI-368} is assigned as Kepler Object of Interesting in the 
\citep{Batalha:2013} from the Quarter 1-6 data. It has a Kepler Input Catalog (KIC) 
entry 6603043. The KIC parameters of the star are $T_{\rm eff} = 9034 {\rm K}$,  
$\rm logg=4.133$, and $\rm FeH = -0.028$, indicating it is a hot and 
fast rotating star. The transit parameter from Kepler catalog is 
$P = 110.3216019 day$ and $R=19.16$\rearth.
We make use of the public Kepler Long Cadence (29.4min) (Q1-Q15) and 
Short Cadence (58.84s) data (Q8-Q9) to study the photometry effect 
predicted by \citet{Barnes:2009}.
The long cadence \lcs consist of 11 transit althogether (assigned transit 
number from epoch 0-11, the 7th transit is not observed by Kepler due to data gap). 
The short cadence \lcs has transit 5 and 6.

For transit fitting, we use the $\rm SAP\_FLUX$, the out of transit 
variations are corrected by the following steps from \citet{Huang:2013}:

a) removal of bad data points;

b) correction of safe mode and tweaks;

c) a set of cosine functions with minimum period of 1 day.

d) a 7th order polynomial fit on the out of transit parts.

For analysis of the rotation period of the star, we use the Q1-Q9 
$\rm PDC\_FLUX$ \citep{Smith:2012} calibrated by the Kepler team.

{\bf TBD: the figure of the lightcurve itself?}

%The gravity darkening model

The gravity darkening model is generatied following 
\citet{Barnes:2009}
The temperature profile on the stellar surface is determined by the local 
effective gravity.
\begin{equation}
\frac{T}{T_{\rm pole}} \propto (\frac{g_{\rm eff}}{g_{\rm pole}})^{\beta}. 
= F_{f,w} (r,\theta).
\end{equation}
f is the oblation of the star, defined as 
$\frac{R_{\rm eq}-R{\rm pole}}{R_{\rm eq}}$. $w$ is the nondimension 
measure of the rotation rate ($w=\Omega_{ror}/\Omega_{grav}$, in which 
$\Omega_{\rm ror}$ is the stellar rotation rate in radians per second, 
$\Omega_{\rm grav}$ is the agular velocity due to gravity at the equator, 
$\Omega_{\rm grav}^2 = GM/R_{\rm eq}$). r and $\theta$ are the normalized 
the position parameters. We use the gravity darkening coefficient computed 
for Kepler band using ATLAS code from \citet{Claret:2011}. By assuming the 
distribution of errors in the stellar parameters to be gaussian, we obtain 
the gravity darkening parameter $\beta$ to be ?.

% \begin{figure}[h!]
%   \centering
%   \includegraphics[width=5cm]{obliq_model.eps}
%   \caption{caption}
%   \label{fig:obliq_model}
% \end{figure}
\begin{figure}
  \centering
  \includegraphics[width=9cm]{obliq_model.eps}
  \caption{caption}
  \label{fig:obliqmodel}
\end{figure}

@@

We use the flux weighted first momentum centroids produced by Kepler 
pipeline to rule out the background binary sinario. In Figure \ref{}

\begin{figure}
\includegraphics[width=0.9\linewidth]{TTV.eps}
\end{figure}

\begin{figure}
\subfigure[]
{
\includegraphics[width=0.45\linewidth]{APOimage.eps}
\label{fig:APO}
}
\subfigure[]{
\includegraphics[width=0.45\linewidth]{centroid.eps}
\label{fig:centroid}
}
\end{figure}
\section{Discussion}
\label{sec:discussion}
